---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)
```

# fecalcanuga

<!-- badges: start -->

[![License: CC BY
4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

<!-- badges: end -->

The goal of `fecalcanuga` is to provide data representing 5 months of field work from April - June 2023 (Canada) and January - February 2024 (Uganda) collecting household and commercial wastewater containment data and characterizing physical, chemical and greenhouse gas data for 22 non-sewered sanitation sites on southern Vancouver island and the southern gulf islands in British Columbia, Canada and 19 sites in Kampala, Uganda.

## Installation

You can install the development version of fecalcanuga from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kelseyshaw/fecalcanuga")
```

```{r}
## Run the following code in console if you don't have the packages
## install.packages(c("dplyr", "knitr", "readr", "stringr", "gt", "kableExtra"))
library(dplyr)
library(knitr)
library(readr)
library(stringr)
library(gt)
library(kableExtra)
```

Alternatively, you can download the individual datasets as a CSV or XLSX
file from the table below.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

extdata_path <- "https://github.com/kelseyshaw/fecalcanuga/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  dplyr::mutate(file_name = str_remove(file_name, ".rda")) |> 
  dplyr::rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()

```

## Data

The package provides access to 4 datasets: `containment`, `ghg`, `household_survey`, and `phys_chem_parameter`.

```{r}
library(fecalcanuga)
```

### containment

The dataset `containment` contains data about the technical data (containment size, volume, fecal sludge depth, etc.) for each non-sewered sanitation system containment that was sampled as a part of this field work. It has `r nrow(containment)` observations and `r ncol(containment)` variables

```{r}
containment |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

For an overview of the variable names, see the following table.

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "containment.rda") |>
  dplyr::select(variable_name:description) |> 
  knitr::kable() |> 
  kableExtra::kable_styling("striped") |> 
  kableExtra::scroll_box(height = "200px")
```

### ghg

The dataset `ghg` contains data about the calculated mass flux rates from the measured point-source in situ GHG measurments and the observed person equivalents for each containment for the three key greenhouse gases (CH4, CO2 and N2O).
It has `r nrow(ghg)` observations and `r ncol(ghg)` variables

```{r}
ghg |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

For an overview of the variable names, see the following table.

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "ghg.rda") |>
  dplyr::select(variable_name:description) |> 
  knitr::kable() |> 
  kableExtra::kable_styling("striped") |> 
  kableExtra::scroll_box(height = "200px")
```

### household_survey

The dataset `household_survey` contains data about the collected household / institutional survey data for each location where a non-sewered sanitation containmenet was sampled. This includes demographic infromation, operational and maintenance information and some technical and environmental parameters.
It has `r nrow(household_survey)` observations and `r ncol(household_survey)` variables

```{r}
household_survey |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

For an overview of the variable names, see the following table.

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "household_survey.rda") |>
  dplyr::select(variable_name:description) |> 
  knitr::kable() |> 
  kableExtra::kable_styling("striped") |> 
  kableExtra::scroll_box(height = "200px")
```

### phys_chem_parameter

The dataset `phys_chem_parameter` contains data about the measured in situ and analyzed in laboratory physical, chemical and biological parameters pertaining to each containment sampled as well as at different veritcal locations in each containment (i.e., Top of containment, middle and bottom).
It has `r nrow(phys_chem_parameter)` observations and `r ncol(phys_chem_parameter)` variables

```{r}
phys_chem_parameter |> 
  head(3) |> 
  gt::gt() |>
  gt::as_raw_html()
```

For an overview of the variable names, see the following table.

```{r echo=FALSE, message=FALSE, warning=FALSE}
readr::read_csv("data-raw/dictionary.csv") |>
  dplyr::filter(file_name == "phys_chem_parameter.rda") |>
  dplyr::select(variable_name:description) |> 
  knitr::kable() |> 
  kableExtra::kable_styling("striped") |> 
  kableExtra::scroll_box(height = "200px")
```


## Example

```{r}
library(fecalcanuga)

# Provide some example code here
```


## License

Data are available as
[CC-BY](https://github.com/openwashdata/fecalcanuga/blob/main/LICENSE.md).

## Citation

Please cite this package using:

```{r}
citation("fecalcanuga")
```
