---
title: "Fecal Sludge Data Analysis"
date: "2024-04-08"
author: "Kelsey Shaw"
format: html
editor: visual
---

# Project Description

This data represents 5 months of field work from April - June 2023 (Canada) and January - February (Uganda) collecting household and commercial wastewater containment data and characterizing physical, chemical and greenhouse gas data for 22 non-sewered sanitation sites on southern Vancouver island and the southern gulf islands in British Columbia, Canada and 19 sites in Kampala, Uganda.

## Load Packages

```{r}
library(readxl)
library(here)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidyr)
library(knitr)
library(gt)
library(gtsummary)
library(DT)
library(reshape2)
library(GGally)
library(plotly)

```

## Import Data

```{r}
head(containment)
#Set working directory
#setwd("/cloud/project/inst/extdata")

#read in cleaned data
#household_survey_data <- read_excel(("fecalcanuga.xlsx"), sheet = 1)
#containment_data <- read_excel(("fecalcanuga.xlsx"), sheet = 2)
#ghg_data <- read_excel(("fecalcanuga.xlsx"), sheet = 3)
#phys_chem_parameter_data <- read_excel(("fecalcanuga.xlsx"), sheet = 4)


# Check first 5 rows
#head(household_survey_data)
#head(containment_data)
#head(ghg_data)
#head(phys_chem_parameter_data)
```
